---
title: "Upgrading packrat"
author: "ShunHasegawa"
date: "Monday, June 30, 2014"
output: html_document
---

This document describes how to upgrade `packrat` for recent update in June 2014. Firstly, delate `.Rprofile`. Then install the up-to-date `packrat`. Also look at <https://github.com/rstudio/packrat/issues/111>.

```{r, eval=FALSE}
if (!require("devtools")) install.packages("devtools")
devtools::install_github("rstudio/packrat", ref = "feature/source-repos")
```

Then, update previous packrat dependent files for upgraded version by running:

```{r, eval=FALSE}
packrat::migrate()
```

Then, check status by `packrat::status()`, and follow the returend instructions. Such packages as `knitr`, `rmarkdown` are not called but need installing. Hence every time when you look at `packrat::status`, you get something like:

```
The following packages have been updated in your library, but have not been recorded in packrat:
                library   packrat
    htmltools     0.2.4        NA
    rmarkdown    0.2.49        NA
    yaml         2.1.13        NA

Use packrat::snapshot() to record these packages in packrat.
```

You can leave it as it is, but if you want to remove, create a .R file, "UncalledPckg.R" for example, and (pretend to) call those packages there.

## Packages not available on CRAN or github
The sources of those packages that are not on CRAN or github (e.g. "HIEv") can't be obtained via `packrat`. Hence, you'd better install them directly to your local directory, otherwise you may have troubles with updating your personal library by `packrat::snapshot()` when you add new packages. You need to use `packrat::extlib("Private.package.Name")` to call them in your script.
